---
title: "Introduction to FASR data"
author: "John Adams"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS package Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo = FALSE, include = FALSE}
library(dplyr)
library(maps)
```

The farsr library contains functions for the reading and displaying of FARS data.

A FARS data file contains data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

The library requires dplyr, tidyr, readr, maps, and graphics.


## Functions

`fars_map_state`          Plots location of accidents on a map.

`fars_read`               Read FARS file

`fars_read_years`         Reads months and years from multiple FARS files (for multiple years)

`fars_summarize_years`    Reads months and years from FARS files and summarizes how many accidents occurred per month/year

`make_filename`           Create a FARS filename for a particular year


## Examples

### fars_read()
```{r eval=FALSE}
fars_read("accident_2015.csv.bz2")
```
```{r example1, results = "asis", echo=FALSE}
setwd(system.file("extdata", package = "farsr"))
knitr::kable(head(fars_read("accident_2015.csv.bz2")))
```

### make_filename()
```{r example2}
setwd(system.file("extdata", package = "farsr"))
make_filename(2015)
```

### fars_read_years()
```{r example3}
setwd(system.file("extdata", package = "farsr"))
fars_read_years(2013:2015)
fars_read_years(list(2013, 2015))
```
### fars_summarize_years()
```{r example4}
setwd(system.file("extdata", package = "farsr"))
fars_summarize_years(2013:2015)
```

## fars_map_state()
```{r example5, fig.show='hold' }
setwd(system.file("extdata", package = "farsr"))
fars_map_state(1, 2013)
```


